Fusion Moves for Correlation Clustering

### 2014-11-13 paper/egpaper_for_review.tex
update 4.1

\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, still NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $y$ the original graph $G=(V,E)$ by
%
\begin{align}
y_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}
Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.

@@

\begin{theorem}[Equivalence]\label{thm:Equivalence}
The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}'$, which is by definition a feasible for~\ref{eq:fusion_move_a}.
If $y'$ would not be an optimal solution than there must exists $y''$ with 
$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
\begin{align*}
  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
 &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
  = \sum_{e\in E} w_ey_e' \\
 &> \sum_{e\in E} w_ey_e''
  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
\end{align*}
where $\bar{y}''$ is the projection from $y''$ on $G_y$.
This contradicts that $y'$ is a optimal segmentation of $G_y$.
\end{proof}
%
\end{theorem}

>>>>

\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ the original graph $G=(V,E)$ by
%
\begin{align}
\tilde{y}_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}

@@

\begin{theorem}[Equivalence]\label{thm:Equivalence}
The back projection of the optimal segmentation $\bar{y}'$ of the contracted graph $G_y=(V_y,E_y, \bar{w})$
is an optimal solution of problem~\ref{eq:fusion_move_a}.
\begin{proof}
Let $y'$ be the back propagation of $\bar{y}'$, which is by definition feasible for~\ref{eq:fusion_move_a}.
If $y'$ would not be an optimal solution than there must exists $y''$ with 
$\sum_{e\in E} w_ey_e' > \sum_{e\in E} w_ey_e''$.
Since $y_e'$ and $y_e''$ are $0$ for all $e \in \mathcal{E}_0^{\breve{y}}$ we would have
\begin{align*}
  \sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}'_{\bar{e}}
 &= \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e'          
  = \sum_{e\in E} w_ey_e' \\
 &> \sum_{e\in E} w_ey_e''
  = \sum_{e\in E \setminus \mathcal{E}_0^{\breve{y}}} w_ey_e''
  =\sum_{\bar{e}\in E_y} \bar{w}_{\bar{e}}\bar{y}''_{\bar{e}}
\end{align*}
where $\bar{y}''$ is the projection from $y''$ on $G_y$.
This contradicts that $y'$ is a optimal segmentation of $G_y$.
\end{proof}
%
\end{theorem}
